\chapter{Objective\\
\small{\textit{-- Nikhil Kumar G, Raj Palival}}
\index{Chapter!Objective}
\index{Objective}
\label{Chapter::Objective}}

\section{OpenCV\label{openCVObjective}}
The objective of OpenCV architecture is to provide a flexible and modular framework for computer vision applications \cite{sampleArch}. The architecture is designed to be highly customizable and extensible, allowing developers to easily integrate new functionalities and algorithms into their applications. The architecture also provides a set of core modules that cover a wide range of computer vision tasks, such as image processing, feature detection, object recognition, and machine learning.\\These modules are designed to be efficient and optimized for performance, making them suitable for real-time applications. Additionally, the architecture provides a user-friendly interface and intuitive APIs that make it easy for developers to interact with the library and implement their computer vision projects. Overall, the objective of OpenCV architecture is to provide a powerful and flexible tool for computer vision applications that can be tailored to meet the specific needs and requirements of each project. 
\index{modular framework} \index{APIs}\index{pairwise stitching}\index{multi-band blending}\index{multi-row stitching}\index{user-friendly interface}
\section{OpenCV Image-Stitching Module\label{imageStitchObjective}}
The objective of the OpenCV image stitching module is to provide a set of tools and algorithms for stitching multiple images together to create a panoramic image. The module is designed to be efficient and optimized for performance, making it suitable for real-time applications. The module provides a set of core functionalities, such as feature detection, feature matching, and image blending, that are used to align and blend the input images into a seamless panoramic image.\\
\\The module also provides various stitching methods, such as pairwise stitching, multi-row stitching, and multi-band blending, that can be used to achieve different levels of quality and performance. Additionally, the module provides a user-friendly interface and intuitive APIs that make it easy for developers to interact with the library and implement their image stitching projects. Overall, the objective of the OpenCV image stitching module is to provide a powerful and flexible tool for creating panoramic images that can be tailored to meet the specific needs and requirements of each project.