\chapter{Stakeholders\\
\small{\textit{-- Nikhil Kumar G, Raj Palival}}
\index{Chapter!Stakeholders}
\index{Stakeholders}
\label{Chapter::Stakeholders}}

\section{Introduction \label{Section::StakeholdersIntroduction}}
In this chapter, we are going to learn about the stakeholders of Open CV. Stakeholders in general for OpenCV can be classified as people or roles who are affected, in some way, by OpenCV. Also, it's worth noting that stakeholders may vary over time as the OpenCV community and ecosystem evolve.

\section{Types of Stakeholders \label{Section::StakeholdersType}}
We will try to group the stakeholders of OpenCV into two broad categories:
\begin{enumerate}
     \item OpenCV Builders
     \item OpenCV Users
 \end{enumerate}
 
\subsection{OpenCV Builders \label{subSection::OpenCVBuilders}}
These stakeholders are involved in developing, maintaining, and enhancing the OpenCV library. They contribute to its code-base, research and implement new algorithms, and ensure its continuous development. The potential stakeholders involved in building OpenCV are:
\begin{enumerate}
     \item Developers
     \item Contributors
     \item OpenCV Foundation
     \item Open-Source community
 \end{enumerate}

 \subsection{OpenCV Users \label{subSection::OpenCVUsers}}
These stakeholders utilize the OpenCV library for various computer vision tasks and applications. They leverage the functionality provided by OpenCV in their projects, products, or services. They can be sub-divided into an exhaustive list. Hence, the potential stakeholders involved in using OpenCV are:
\begin{enumerate}
     \item End-Users
     \item Researchers
     \item Academic institutions
     \item Industry partners
     \item Government agencies
 \end{enumerate}
\index{OpenCV Foundation}\index{Open-Source community}\index{End-Users}\index{Researchers}\index{Academic institutions} \index{Industry partners}\index{Government agencies}\index{bug reports}
\begin{table} [H]
\begin{tabular}{|c|m{11.4cm}|} 
\hline
\textbf{STAKEHOLDERS} & \textbf{DESCRIPTION} \\ \hline
Developers & Developers are the core team responsible for actively developing, maintaining, and enhancing the OpenCV library's source code and features. \\ \hline 

Contributors & They are individuals or organizations who support the project by providing bug reports, feedback, documentation, tutorials, and code changes, helping to improve and expand its functionality. \\ \hline 

OpenCV Foundation & The organization responsible for managing and overseeing the development and maintenance of the OpenCV library, ensuring its long-term sustainability and growth. \\ \hline 

Open-Source Community & The broader community of developers, enthusiasts, and users who provide feedback, support, and contribute to the improvement and expansion of OpenCV. \\ \hline 

End-Users & The ultimate beneficiaries or users of the project's outcome, who will interact with the OpenCV-based functionalities directly or indirectly. \\ \hline 

Researchers & Professionals and academics who employ OpenCV in their research work, leveraging its computer vision algorithms and functionalities. \\ \hline 

Academic Institutions & Universities and research institutes that incorporate OpenCV into their computer vision courses and projects, helping educate future computer vision professionals. \\ \hline 

Industry Partners & Companies and organizations that integrate OpenCV into their products, services, or platforms, enabling computer vision capabilities. \\ \hline 

Government Agencies & Public sector organizations that may utilize OpenCV for various purposes, such as surveillance, image analysis, or research initiatives. \\ \hline 
\end{tabular}
\caption{Stakeholders' description \label{Table::StakeholdersDescription}}
\end{table}
