\chapter{User Requirements\\
\small{\textit{-- Nikhil Kumar G, Raj Palival}}
\index{Chapter!User Requirements}
\index{User Requirements}
\label{Chapter::User Requirements}}

\section{What is a User Requirement? \label{Section::UserRequirementsIntroduction}}
In this chapter, we are going to learn about the 'User Requirements' of OpenCV. User requirements are detailed and specific statements that outline the functionality, constraints, and qualities expected from a system or product. 

\section{User Requirements of OpenCV \label{Section::UserRequirements}}
Users often have certain expectations and needs when utilizing OpenCV in their projects. Some common user requirements of OpenCV can include:
\begin{longtable}{| p{.21\textwidth} | p{.79\textwidth} |} 
\hline
\textbf{User requirements} & \textbf{Description}  \\ \hline
Versatile Image and Video Processing & Users expect OpenCV to provide a wide range of image and video processing capabilities, such as image filtering, resizing, color space conversions, object detection, and tracking. \\ \hline 
Efficient and Optimized Algorithms & Users require efficient and optimized algorithms implemented in OpenCV, enabling fast and accurate computer vision operations even on resource-constrained devices. \\ \hline
Robust and Accurate Functions & Users depend on OpenCV to deliver reliable and accurate computer vision functions, such as feature extraction, pattern recognition, image segmentation, and optical flow analysis. \\ \hline
Documentation and Support & Users look for comprehensive documentation, tutorials, and examples that help them understand and effectively use the OpenCV library. They also appreciate active community support, forums, and resources that assist in troubleshooting and problem-solving. \\ \hline
Cross-Platform Compatibility & Users expect OpenCV to work seamlessly across different platforms and operating systems, including Windows, macOS, Linux, Android, and iOS. \\ \hline
Integration with Libraries and Frameworks & Users often require OpenCV to integrate smoothly with other libraries and frameworks commonly used in computer vision and machine learning, such as NumPy, TensorFlow, and PyTorch. \\ \hline
Flexibility and Customization & Users appreciate the ability to customize and extend OpenCV to suit their specific project requirements, including the option to add new algorithms, modify existing functions, or interface with specialized hardware. \\ \hline
Performance Optimization Tools & Users often require tools and techniques to optimize the performance of OpenCV-based applications, including multi-threading, GPU acceleration, and code profiling. \\ \hline
License Compatibility & Users may have specific requirements regarding the licensing of OpenCV to ensure compliance with their project's open-source or commercial license obligations. \\ \hline
Real-Time Camera & Users require OpenCV to provide seamless integration with cameras and enable real-time capture and processing of camera input. \\ \hline 
\caption{User Requirements \label{Table::UserRequirements}}
\end{longtable}

These user stories demonstrate the diverse range of users and their specific needs when utilizing OpenCV for various applications, spanning from research and development to commercial projects and personal interests.